---
title: "Prediction of stroke"
output: html_document
date: "2022-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Null hypothesis: 
#There is no relationship between the variables like gender, age, various diseases, and smoking status and stroke, the 2nd leading cause of death.

#According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths.
#This dataset is used to predict whether a patient is likely to get stroke based on the input parameters like gender, age, various diseases, and smoking status. Each row in the data provides relavant information about the patient.
#Attribute Information

#1) id: unique identifier
#2) gender: "Male", "Female" or "Other"
#3) age: age of the patient
#4) hypertension: 0 if the patient doesn't have hypertension, 1 if the patient has hypertension
#5) heart_disease: 0 if the patient doesn't have any heart diseases, 1 if the patient has a heart disease
#6) ever_married: "No" or "Yes"
#7) work_type: "children", "Govt_jov", "Never_worked", "Private" or "Self-employed"
#8) Residence_type: "Rural" or "Urban"
#9) avg_glucose_level: average glucose level in blood
#10) bmi: body mass index
#11) smoking_status: "formerly smoked", "never smoked", "smokes" or "Unknown"*
#12) stroke: 1 if the patient had a stroke or 0 if not
#*Note: "Unknown" in smoking_status means that the information is unavailable for this patient

```{r}

getwd()
Stroke_dataset <- read.csv("/Users/nehabhasin/Desktop/HS631-STATS/PREDICTION OF STROKE_PROJECT/prediction_of_stroke-project_1/data/Stroke_dataset.csv",header = TRUE, sep = ",")

head(Stroke_dataset)
str(Stroke_dataset)

any(is.na(Stroke_dataset))
colSums(is.na(Stroke_dataset))

```


```{r}

summary(Stroke_dataset)
Stroke_dataset$bmi[is.na(Stroke_dataset$bmi)] <- 0
Stroke_dataset$bmi[Stroke_dataset$bmi==0] <- sample(23.50:28.89,replace=TRUE)

```

