---
title: "Prediction of stroke"
output: html_document
date: "2022-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Null hypothesis: 
#There is no relationship between the variables like gender, age, various diseases, and smoking status and stroke, the 2nd leading cause of death.

#According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths.
#This dataset is used to predict whether a patient is likely to get stroke based on the input parameters like gender, age, various diseases, and smoking status. Each row in the data provides relavant information about the patient.
#Attribute Information

#1) id: unique identifier
#2) gender: "Male", "Female" or "Other"
#3) age: age of the patient
#4) hypertension: 0 if the patient doesn't have hypertension, 1 if the patient has hypertension
#5) heart_disease: 0 if the patient doesn't have any heart diseases, 1 if the patient has a heart disease
#6) ever_married: "No" or "Yes"
#7) work_type: "children", "Govt_jov", "Never_worked", "Private" or "Self-employed"
#8) Residence_type: "Rural" or "Urban"
#9) avg_glucose_level: average glucose level in blood
#10) bmi: body mass index
#11) smoking_status: "formerly smoked", "never smoked", "smokes" or "Unknown"*
#12) stroke: 1 if the patient had a stroke or 0 if not
#*Note: "Unknown" in smoking_status means that the information is unavailable for this patient

Chunk 1:(Neha-changes in chunk1 to chunk24)
```{r}
#Reading the dataset and checking for NA's.

getwd()
Stroke_dataset <- read.csv("/Users/nehabhasin/Desktop/HS631-STATS/PREDICTION OF STROKE_PROJECT/prediction_of_stroke-project_1/data/Stroke_dataset.csv",header = TRUE, sep = ",")

head(Stroke_dataset)
str(Stroke_dataset)

any(is.na(Stroke_dataset))
colSums(is.na(Stroke_dataset))

```

Chunk 2:
```{r}
#Summarising the data and replacing the NA's in the dataset with appropriate values.

summary(Stroke_dataset)
Stroke_dataset$bmi[is.na(Stroke_dataset$bmi)] <- 0
Stroke_dataset$bmi[Stroke_dataset$bmi==0] <- sample(23.50:28.89,replace=TRUE)

```

Chunk 3:
```{r}
#Plotting frequency distribution curve.

hist(Stroke_dataset$age,col="lavender",border="black",prob=TRUE,xlab="Age group",main="Distribution of patients")
lines(density(Stroke_dataset$age),lwd=2,col="red")

```

Chunk 4:
```{r}
#Categorizing age in different groups.

Stroke_dataset$age_cat[Stroke_dataset$age>=0 & Stroke_dataset$age<11]="0-10"
Stroke_dataset$age_cat[Stroke_dataset$age>=11 & Stroke_dataset$age<21]="11-20"
Stroke_dataset$age_cat[Stroke_dataset$age>=21 & Stroke_dataset$age<31]="21-30"
Stroke_dataset$age_cat[Stroke_dataset$age>=31 & Stroke_dataset$age<41]="31-40"
Stroke_dataset$age_cat[Stroke_dataset$age>=41 & Stroke_dataset$age<51]="41-50"
Stroke_dataset$age_cat[Stroke_dataset$age>=51 & Stroke_dataset$age<61]="51-60"
Stroke_dataset$age_cat[Stroke_dataset$age>=61 & Stroke_dataset$age<71]="61-70"
Stroke_dataset$age_cat[Stroke_dataset$age>=71 & Stroke_dataset$age<81]="71-80"
Stroke_dataset$age_cat[Stroke_dataset$age>=81 & Stroke_dataset$age<91]="81-90"

#Plotting different age groups with absence and presence of stroke.

Age_vs_Stroke <- table(Stroke_dataset$age_cat,Stroke_dataset$stroke)
Age_vs_Stroke
A <- barplot(Age_vs_Stroke, main="Relation between age and stroke",xlab="Stroke",ylim=range(pretty(c(0,Age_vs_Stroke))),col=rainbow(9),names.arg=c("absent","present"), legend=TRUE , args.legend = list(title = "Age groups", x="topright"), beside= TRUE)
text(x=A,y=Age_vs_Stroke + 20.0,labels=Age_vs_Stroke)

```

Chunk 5:
```{r}
#Plotting gender distribution against stroke.

as.factor(Stroke_dataset$gender)

Gender_vs_Stroke <- table(Stroke_dataset$gender,Stroke_dataset$stroke)
Gender_vs_Stroke
G <- barplot(Gender_vs_Stroke, main="Relation between gender and stroke", xlab="Stroke",ylim=range(pretty(c(0,Gender_vs_Stroke))),ylab="No. of patients",col=c("aquamarine","forestgreen","lightgreen"), names.arg=c("absent","present"),beside= TRUE, legend=c("Female","Male","Other"),args.legend = list(title = "Gender", x="topright"))
text(x=G,y=Gender_vs_Stroke + 100.0,labels=Gender_vs_Stroke)

```

Chunk 6:
```{r}
#Plotting patients with/without hypertension and stroke.

Hypertension_vs_Stroke <- table(Stroke_dataset$hypertension,Stroke_dataset$stroke)
Hypertension_vs_Stroke
HTN <- barplot(Hypertension_vs_Stroke, main="Relation between hypertension and stroke", xlab="Stroke",ylim=range(pretty(c(0,Hypertension_vs_Stroke))),ylab="No. of patients",col=c("springgreen","seagreen"), names.arg=c("absent","present"),beside= TRUE, legend=c("absent","present"),args.legend = list(title = "Hypertension", x="topright"))
text(x=HTN,y=Hypertension_vs_Stroke + 200.0,labels=Hypertension_vs_Stroke)

```

Chunk 7:
```{r}
#Plotting heart disease vs stroke.

Heart_Disease_vs_Stroke <- table(Stroke_dataset$heart_disease,Stroke_dataset$stroke)
Heart_Disease_vs_Stroke
HD <- barplot(Heart_Disease_vs_Stroke, main="Relation between heart disease and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Heart_Disease_vs_Stroke))), col=c("lightyellow","yellow"),names.arg=c("absent","present"), legend=c("absent","present"), args.legend = list(title = "Heart disease", x="topright"), beside= TRUE)
text(x=HD,y=Heart_Disease_vs_Stroke + 200.0,labels=Heart_Disease_vs_Stroke)

```

Chunk 8:
```{r}
#Categorizing avg_glucose_level in three groups based on their blood sugar levels as non-diabetic(0), pre-diabetic(1) and diabetic(2)

Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level<140] = 0
Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level>=140 & Stroke_dataset$avg_glucose_level<200] = 1
Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level>=200] = 2

#Plotting non-diabetic, pre-diabetic and diabetic groups with absence or presence of stroke.

Diabetes_vs_Stroke <- table(Stroke_dataset$avg_glucose_level_cat,Stroke_dataset$stroke)
Diabetes_vs_Stroke
D <- barplot(Diabetes_vs_Stroke, main="Relation between diabetes and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Diabetes_vs_Stroke))), col=c("lavender","violet","purple"),names.arg=c("absent","present"), legend=c("non-diabetic","pre-diabetic","diabetic"), beside= TRUE)
text(x=D,y=Diabetes_vs_Stroke + 200.0,labels=Diabetes_vs_Stroke)

```

Chunk 9:
```{r}
#Plotting relation of smoking and stroke.

as.factor(Stroke_dataset$smoking_status)

Smoking_status_vs_Stroke <- table(Stroke_dataset$smoking_status,Stroke_dataset$stroke)
Smoking_status_vs_Stroke
z <- barplot(Smoking_status_vs_Stroke, main="Relation between smoking and stroke", xlab="Stroke",ylab="No. of patients", ylim=range(pretty(c(0,Smoking_status_vs_Stroke))), col=c("lightcyan","lightblue","blue","navyblue"),names.arg=c("absent","present"), legend=c("formerly smoked","never smoked","smokes","unknown"), args.legend = list(title = "Smoking status", x="topright"), beside= TRUE)
text(x=z,y=Smoking_status_vs_Stroke + 100.0,labels=Smoking_status_vs_Stroke)

```
Chunk 10:
```{r}
#Plotting relation between marriage status and stroke.

Stroke_dataset$ever_married <- as.factor(Stroke_dataset$ever_married)
Stroke_dataset$ever_married <- as.numeric(Stroke_dataset$ever_married)

Marriage_vs_Stroke <- table(Stroke_dataset$ever_married,Stroke_dataset$stroke)
Marriage_vs_Stroke
M <- barplot(Marriage_vs_Stroke, main="Relation between marriage status and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Marriage_vs_Stroke))), col=c("red","yellow"),names.arg=c("absent","present"), legend=c("No","Yes"), args.legend = list(title = "Ever Married", x="topright"), beside= TRUE)
text(x=M,y=Marriage_vs_Stroke + 200.0,labels=Marriage_vs_Stroke)

```
Chunk 11:
```{r}
#Plotting relation between working status and stroke.

Stroke_dataset$work_type <- as.factor(Stroke_dataset$work_type)
Stroke_dataset$work_type <- as.numeric(Stroke_dataset$work_type)

Work_type_vs_Stroke <- table(Stroke_dataset$work_type,Stroke_dataset$stroke)
Work_type_vs_Stroke
WT <- barplot(Work_type_vs_Stroke, main="Relation between working status and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Work_type_vs_Stroke))), col=rainbow(5),names.arg=c("absent","present"), legend=c("child","government job","never worked","private","self-employed"), args.legend = list(title = "Working status", x="topright"), beside= TRUE)
text(x=WT,y=Work_type_vs_Stroke + 100.0,labels=Work_type_vs_Stroke)

```

Chunk 12:
```{r}
#Plotting relation between residence type and stroke.

Stroke_dataset$Residence_type <- as.factor(Stroke_dataset$Residence_type)
Stroke_dataset$Residence_type <- as.numeric(Stroke_dataset$Residence_type)

Residence_vs_Stroke <- table(Stroke_dataset$Residence_type,Stroke_dataset$stroke)
Residence_vs_Stroke
R <- barplot(Residence_vs_Stroke, main="Relation between residence type and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Residence_vs_Stroke))), col=c("grey","black"),names.arg=c("absent","present"), legend=c("Rural","Urban"), args.legend = list(title = "Residence", x="topright"), beside= TRUE)
text(x=R,y=Residence_vs_Stroke + 200.0,labels=Residence_vs_Stroke)

```

Chunk 13:
```{r}
#Plotting relation between bmi and stroke.

Stroke_dataset_bmi_adults <- Stroke_dataset[Stroke_dataset$age>20 & Stroke_dataset$age<=85,]
Stroke_dataset_bmi_adults

Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi<18.5]="underweight"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=18.5 & Stroke_dataset_bmi_adults$bmi<25]="healthy"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=25 & Stroke_dataset_bmi_adults$bmi<30]="overweight"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=30]="obese"

BMI_vs_Stroke <- table(Stroke_dataset_bmi_adults$bmi_cat,Stroke_dataset_bmi_adults$stroke)
BMI_vs_Stroke
bmi <- barplot(BMI_vs_Stroke, main="Relation between BMI and stroke",xlab="Stroke",ylim=range(pretty(c(0,BMI_vs_Stroke))),col=c("pink","orange","red","yellow"),names.arg=c("absent","present"), legend=TRUE , args.legend = list(title = "BMI", x="topright"), beside= TRUE)
text(x=bmi,y=BMI_vs_Stroke + 100.0,labels=BMI_vs_Stroke)

```
Chunk 14:
```{r}
#Applying chi-square test to find an association between different categorical independent variables and the dependent variable(stroke).
#Gender vs Stroke

chisq.test(Stroke_dataset$gender,Stroke_dataset$stroke)

```

Chunk 15:
```{r}
#Hypertension vs Stroke
chisq.test(Stroke_dataset$hypertension,Stroke_dataset$stroke)
```

Chunk 16:
```{r}
#Heart disease vs Stroke
chisq.test(Stroke_dataset$heart_disease,Stroke_dataset$stroke)
```

Chunk 17:
```{r}
#Marriage status vs Stroke
chisq.test(Stroke_dataset$ever_married,Stroke_dataset$stroke)
```

Chunk 18:
```{r}
#Working status vs Stroke
chisq.test(Stroke_dataset$work_type,Stroke_dataset$stroke)
```

Chunk 19:
```{r}
#Residence type vs Stroke
chisq.test(Stroke_dataset$Residence_type,Stroke_dataset$stroke)
```

Chunk 20:
```{r}
#Smoking status vs Stroke
chisq.test(Stroke_dataset$smoking_status,Stroke_dataset$stroke)
```

Chunk 21:
```{r}
#Finding correlation between different continuous independent variables and the dependent variable(stroke).
#Age vs Stroke
cor.test(Stroke_dataset$age,Stroke_dataset$stroke)
```

Chunk 22:
```{r}
#BMI vs Stroke
cor.test(Stroke_dataset$bmi,Stroke_dataset$stroke)
```

Chunk 23:
```{r}
#Diabetes vs Stroke
cor.test(Stroke_dataset$avg_glucose_level,Stroke_dataset$stroke)
```

Chunk 24:
```{r}
#Correlation matrix

Stroke_dataset <- read.csv("/Users/nehabhasin/Desktop/HS631-STATS/PREDICTION OF STROKE_PROJECT/prediction_of_stroke-project_1/data/Stroke_dataset.csv",header = TRUE, sep = ",")
colSums(is.na(Stroke_dataset))
Stroke_dataset$bmi[is.na(Stroke_dataset$bmi)] <- 0
Stroke_dataset$bmi[Stroke_dataset$bmi==0] <- sample(23.50:28.89,replace=TRUE)

Stroke_dataset$gender <- as.factor(Stroke_dataset$gender)
Stroke_dataset$ever_married <- as.factor(Stroke_dataset$ever_married)
Stroke_dataset$work_type <- as.factor(Stroke_dataset$work_type)
Stroke_dataset$Residence_type <- as.factor(Stroke_dataset$Residence_type)
Stroke_dataset$smoking_status <- as.factor(Stroke_dataset$smoking_status)

Stroke_dataset$smoking_status <- as.numeric(Stroke_dataset$smoking_status)
Stroke_dataset$gender <- as.numeric(Stroke_dataset$gender) 
Stroke_dataset$ever_married <- as.numeric(Stroke_dataset$ever_married)
Stroke_dataset$work_type <- as.numeric(Stroke_dataset$work_type)
Stroke_dataset$Residence_type <- as.numeric(Stroke_dataset$Residence_type)

any(is.na(Stroke_dataset))

rcorr(as.matrix(Stroke_dataset[,2:12]))

Matrix_Stroke <- cor(Stroke_dataset[,2:12])
Matrix_Stroke
corrplot(Matrix_Stroke, method="circle",type="lower",tl.col="black")

```


```{r}
###Swarna(updated)
install.packages("caTools")
install.packages("ggpubr")
install.packages("ggcorrplot")
library(plotly)
library(ggplot2)
library(ggcorrplot)
library(ggpubr)
library(dplyr)
library(VennDiagram)
library(ggbeeswarm)
library(pwr)
library(psych)
library(pastecs)
library(ggm)
library(Hmisc)
library(pwr)
library(car)
library(caTools)
library("MASS")


# Aim to predict if the patient will have stroke
#Does the patient experience stroke
# Null Hypothesis: Patients will not have stroke
#Alternative hypothesis: Patients will have stroke 
#Methodology: Use Multiple logistic regression to predict
#Dependent variable: Stroke
#Independent variables: 10 independent variables
#outcome variable: Stroke
#Quantitative variables: age, avg glucose level, bmi, stroke, sus BP, diaBP, BMI, on admit heart rate
#Categorical: gender, hypertension, heart disease, ever married, work type, residence type, smoking status

#Chunk 1: Read the stroke_dataset file and check for NA's
Stroke <- read.csv("Stroke_dataset.csv",header = TRUE, sep = ",")
any(is.na(Stroke))
Stroke[is.na(Stroke)] <- 0
summary(Stroke)
str(Stroke)


#Chunk 2: Replace the NA values
Stroke <- Stroke[,-15]

Stroke$bmi[Stroke$bmi == 0] <- runif(sum(Stroke$bmi == 0), min = 22.9, max = 32.8)

#Chunk 3: 
Stroke[Stroke$gender == "other",]$gender <- NA
summary(Stroke$gender)
Stroke <- Stroke[!(is.na(Stroke$gender)),]
summary(Stroke$gender)

#Chunk 4: Converting stroke data to Binomial variables
Stroke$gender <- as.factor(Stroke$gender)
Stroke$ever_married <- as.factor(Stroke$ever_married)
Stroke$work_type <- as.factor(Stroke$work_type)
Stroke$Residence_type <- as.factor(Stroke$Residence_type)
Stroke$smoking_status <- as.factor(Stroke$smoking_status)
Stroke$hypertension <- as.factor(Stroke$hypertension)
Stroke$heart_disease <- as.factor(Stroke$heart_disease)
Stroke$stroke <- as.factor(Stroke$stroke)

summary(Stroke)

#Chunk 5: Plotting the variables
#Plot the axis
plot(Stroke$hypertension,Stroke$age)
plot(Stroke$heart_disease,Stroke$age)
plot(Stroke$stroke,Stroke$age)
plot(Stroke$stroke,Stroke$OnAdmit_heartRate)

#plotting for all continuous variables
ggplot(data=Stroke,aes(x=age)) + geom_density()
ggplot(data=Stroke,aes(x=bmi)) + geom_density() #####
ggplot(data=Stroke,aes(x=avg_glucose_level)) + geom_density()####
ggplot(data=Stroke,aes(x=sysBP)) + geom_density()
ggplot(data=Stroke,aes(x=diaBP)) + geom_density()
ggplot(data=Stroke,aes(x=OnAdmit_heartRate)) + geom_density()

#plotting for combination nominal variables (smoking staus, bmi)
ggplot(data=Stroke,aes(x=smoking_status,fill=stroke)) + geom_histogram(stat="count")
ggplot(data=Stroke,aes(x=bmi,fill=stroke)) + geom_density()




#Chunk 6: Log Transformation
Stroke$logbmi <- log(Stroke$bmi)
ggplot(data=Stroke,aes(x=logbmi)) + geom_density()

Stroke$logglucose <- log(Stroke$avg_glucose_level-45)####iterated to 45 for alteast normal distribution
ggplot(data=Stroke,aes(x=logglucose)) + geom_density()

#Chunk 7: Splitting the data to Train data and test data as the sample size is high

split <- sample.split(Stroke$stroke, SplitRatio = 0.8)
TrainStroke <- subset(Stroke,split==TRUE)
TestStroke <- subset(Stroke,split==FALSE)

stat.desc(TrainStroke, basic = FALSE, norm = TRUE)
stat.desc(TestStroke, basic = FALSE, norm = TRUE)

#Chunk 8: Identifying correlation
corr = round(cor(Stroke[,c(3,9,10,13,14,15,16,17)]),2) #rounding to 2 decimal
corr
#none correlated
ggcorrplot(corr,hc.order=TRUE)

#Chunk 9: Applying Logistic regression

strokepredict <- glm(stroke ~ gender + age + hypertension + heart_disease + ever_married + work_type + Residence_type + avg_glucose_level + bmi + smoking_status + sysBP + diaBP + OnAdmit_heartRate + logbmi + logglucose, data = Stroke, family="binomial")
summary(strokepredict)

exp(coef(strokepredict))

##
ll.null <- strokepredict$null.deviance/-2
ll.proposed <- strokepredict$deviance/-2
(ll.null-ll.proposed)/ll.null

1-pchisq(2*(ll.proposed-ll.null),df=(length(strokepredict$coefficients)-1))

predicted.data <- data.frame(probability.of.stroke=strokepredict$fitted.values,stroke = Stroke$stroke)
predicted.data <- predicted.data[order(predicted.data$probability.of.stroke,decreasing=FALSE),]
predicted.data$rank <- 1:nrow(predicted.data)
ggplot(data=predicted.data,aes(x=rank,y=probability.of.stroke))+geom_point(aes(color=stroke),alpha=1,shape=4,stroke=2)

Newstrokepredict <- stepAIC (strokepredict)

ll.null <- Newstrokepredict$null.deviance/-2
ll.proposed <- Newstrokepredict$deviance/-2
(ll.null-ll.proposed)/ll.null

1-pchisq(2*(ll.proposed-ll.null),df=(length(Newstrokepredict$coefficients)-1))

predicted.data1 <- data.frame(probability.of.stroke=Newstrokepredict$fitted.values,stroke = Stroke$stroke)
predicted.data1 <- predicted.data1[order(predicted.data1$probability.of.stroke,decreasing=FALSE),]
predicted.data1$rank <- 1:nrow(predicted.data1)
ggplot(data=predicted.data1,aes(x=rank,y=probability.of.stroke))+geom_point(aes(color=stroke),alpha=1,shape=4,stroke=2)
summary(Newstrokepredict)

ResultStroke <- predict(strokepredict,TestStroke,type="response")

confmatrix <- table(Actualvalue=TestStroke$stroke, Predictedvalue = ResultStroke >0.5)
confmatrix

(confmatrix[[1,1]] + confmatrix[[2,2]])/sum(confmatrix)

ResultStroke <- predict(Newstrokepredict,TestStroke,type="response")

confmatrix <- table(Actualvalue=TestStroke$stroke, Predictedvalue = ResultStroke >0.5)
confmatrix

round (exp(coef(Newstrokepredict)),3)
```

