---
title: "Prediction of stroke"
output: powerpoint_presentation
date: "2022-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Null hypothesis: 
#There is no relationship between the variables like gender, age, various diseases, and smoking status and stroke, the 2nd leading cause of death.

#According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths.
#This dataset is used to predict whether a patient is likely to get stroke based on the input parameters like gender, age, various diseases, and smoking status. Each row in the data provides relavant information about the patient.
#Attribute Information

#1) id: unique identifier
#2) gender: "Male", "Female" or "Other"
#3) age: age of the patient
#4) hypertension: 0 if the patient doesn't have hypertension, 1 if the patient has hypertension
#5) heart_disease: 0 if the patient doesn't have any heart diseases, 1 if the patient has a heart disease
#6) ever_married: "No" or "Yes"
#7) work_type: "children", "Govt_jov", "Never_worked", "Private" or "Self-employed"
#8) Residence_type: "Rural" or "Urban"
#9) avg_glucose_level: average glucose level in blood
#10) bmi: body mass index
#11) smoking_status: "formerly smoked", "never smoked", "smokes" or "Unknown"*
#12) stroke: 1 if the patient had a stroke or 0 if not
#*Note: "Unknown" in smoking_status means that the information is unavailable for this patient


Chunk 1:
```{r}

library(plotly)
library(ggplot2)
library(ggcorrplot)
library(ggpubr)
library(dplyr)
library(VennDiagram)
library(ggbeeswarm)
library(pwr)
library(psych)
library(pastecs)
library(ggm)
library(Hmisc)
library(pwr)
library(car)
library(caTools)
library(MASS)

```

Chunk 2:
```{r}
#Reading the dataset and checking for NA's.

#getwd()
#Stroke_dataset <- read.csv("/Users/nehabhasin/Desktop/HS631-STATS/PREDICTION OF #STROKE_PROJECT/prediction_of_stroke-project_1/data/Stroke_dataset.csv",header = TRUE, sep = ",")

Stroke_dataset <- read.csv("Stroke_dataset.csv",header = TRUE, sep = ",")
head(Stroke_dataset)
str(Stroke_dataset)

any(is.na(Stroke_dataset))
colSums(is.na(Stroke_dataset))

```

Chunk 3:
```{r}
#Summarising the data and replacing the NA's in the dataset with appropriate values.
Stroke <- Stroke[,-15]
summary(Stroke_dataset)
Stroke_dataset$bmi[is.na(Stroke_dataset$bmi)] <- 0
Stroke_dataset$bmi[Stroke_dataset$bmi==0] <- sample(23.50:28.89,replace=TRUE)

```

Chunk 4:
```{r}
###########
Stroke_dataset$gender[Stroke_dataset$gender=="other"] <- NA
summary(Stroke_dataset$gender)
table(Stroke_dataset$gender)
Stroke <- Stroke_dataset[!(is.na(Stroke_dataset$gender)),]
summary(Stroke_dataset$gender)
table(Stroke_dataset$gender)
```

Chunk 5:
```{r}
#Plotting frequency distribution curve using age.

hist(Stroke_dataset$age,col="lavender",border="black",prob=TRUE,xlab="Age group",main="Distribution of patients")
lines(density(Stroke_dataset$age),lwd=2,col="red")

```

Chunk 6:
```{r}
#Plotting frequency distribution curve using BMI.

hist(Stroke_dataset$bmi,col="light blue",border="black",prob=TRUE,xlab="BMI",main="Distribution of patients")
lines(density(Stroke_dataset$bmi),lwd=2,col="red")

```

Chunk 7:
```{r}
#Log Transformation for BMI.

Stroke_dataset$logbmi <- log(Stroke_dataset$bmi)
hist(Stroke_dataset$logbmi,col="light blue",border="black",prob=TRUE,xlab="BMI",main="Distribution of patients")
lines(density(Stroke_dataset$logbmi),lwd=2,col="red")
#ggplot(data=Stroke_dataset,aes(x=logbmi)) + geom_density()

```

Chunk 8:
```{r}
#Plotting frequency distribution curve using average blood glucose levels.

hist(Stroke_dataset$avg_glucose_level,col="light green",border="black",prob=TRUE,xlab="Average Blood Glucose levels",main="Distribution of patients")
lines(density(Stroke_dataset$avg_glucose_level),lwd=2,col="red")

```

Chunk 9:
```{r}
#Log Transformation for average glucose levels.

Stroke_dataset$logglucose <- log(Stroke_dataset$avg_glucose_level-45)####iterated to 45 for alteast normal distribution
hist(Stroke_dataset$logglucose,col="light green",border="black",prob=TRUE,xlab="BMI",main="Distribution of patients")
lines(density(Stroke_dataset$logglucose),lwd=2,col="red")
#ggplot(data=Stroke_dataset,aes(x=logglucose)) + geom_density()

```


Chunk 10:
```{r}
#Categorizing age in different groups.

Stroke_dataset$age_cat[Stroke_dataset$age>=0 & Stroke_dataset$age<46]="0-45"
Stroke_dataset$age_cat[Stroke_dataset$age>=46 & Stroke_dataset$age<91]="46-90"

#Plotting different age groups with absence and presence of stroke.

Age_vs_Stroke <- table(Stroke_dataset$age_cat,Stroke_dataset$stroke)
Age_vs_Stroke
A <- barplot(Age_vs_Stroke, main="Relation between age and stroke",xlab="Stroke",ylim=range(pretty(c(0,Age_vs_Stroke))),col=c("magenta","pink"),names.arg=c("absent","present"), legend=TRUE , args.legend = list(title = "Age groups", x="topright"), beside= TRUE)
text(x=A,y=Age_vs_Stroke + 100.0,labels=Age_vs_Stroke)

```

Chunk 11:
```{r}
#Plotting gender distribution against stroke.

as.factor(Stroke_dataset$gender)

Gender_vs_Stroke <- table(Stroke_dataset$gender,Stroke_dataset$stroke)
Gender_vs_Stroke
G <- barplot(Gender_vs_Stroke, main="Relation between gender and stroke", xlab="Stroke",ylim=range(pretty(c(0,Gender_vs_Stroke))),ylab="No. of patients",col=c("aquamarine","forestgreen"), names.arg=c("absent","present"),beside= TRUE, legend=c("Female","Male"),args.legend = list(title = "Gender", x="topright"))
text(x=G,y=Gender_vs_Stroke + 100.0,labels=Gender_vs_Stroke)

```

Chunk 12:
```{r}
#Plotting patients with/without hypertension and stroke.

Hypertension_vs_Stroke <- table(Stroke_dataset$hypertension,Stroke_dataset$stroke)
Hypertension_vs_Stroke
HTN <- barplot(Hypertension_vs_Stroke, main="Relation between hypertension and stroke", xlab="Stroke",ylim=range(pretty(c(0,Hypertension_vs_Stroke))),ylab="No. of patients",col=c("springgreen","seagreen"), names.arg=c("absent","present"),beside= TRUE, legend=c("absent","present"),args.legend = list(title = "Hypertension", x="topright"))
text(x=HTN,y=Hypertension_vs_Stroke + 200.0,labels=Hypertension_vs_Stroke)

```

Chunk 13:
```{r}
#Plotting heart disease vs stroke.

Heart_Disease_vs_Stroke <- table(Stroke_dataset$heart_disease,Stroke_dataset$stroke)
Heart_Disease_vs_Stroke
HD <- barplot(Heart_Disease_vs_Stroke, main="Relation between heart disease and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Heart_Disease_vs_Stroke))), col=c("lightyellow","yellow"),names.arg=c("absent","present"), legend=c("absent","present"), args.legend = list(title = "Heart disease", x="topright"), beside= TRUE)
text(x=HD,y=Heart_Disease_vs_Stroke + 200.0,labels=Heart_Disease_vs_Stroke)

```

Chunk 14:
```{r}
#Categorizing avg_glucose_level in three groups based on their blood sugar levels as non-diabetic(0), pre-diabetic(1) and diabetic(2)

Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level<140] = 0
Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level>=140 & Stroke_dataset$avg_glucose_level<200] = 1
Stroke_dataset$avg_glucose_level_cat[Stroke_dataset$avg_glucose_level>=200] = 2

#Plotting non-diabetic, pre-diabetic and diabetic groups with absence or presence of stroke.

Diabetes_vs_Stroke <- table(Stroke_dataset$avg_glucose_level_cat,Stroke_dataset$stroke)
Diabetes_vs_Stroke
D <- barplot(Diabetes_vs_Stroke, main="Relation between diabetes and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Diabetes_vs_Stroke))), col=c("lavender","violet","purple"),names.arg=c("absent","present"), legend=c("non-diabetic","pre-diabetic","diabetic"), beside= TRUE)
text(x=D,y=Diabetes_vs_Stroke + 200.0,labels=Diabetes_vs_Stroke)

```

Chunk 15:
```{r}
#Plotting relation of smoking and stroke.

as.factor(Stroke_dataset$smoking_status)

Smoking_status_vs_Stroke <- table(Stroke_dataset$smoking_status,Stroke_dataset$stroke)
Smoking_status_vs_Stroke
z <- barplot(Smoking_status_vs_Stroke, main="Relation between smoking and stroke", xlab="Stroke",ylab="No. of patients", ylim=range(pretty(c(0,Smoking_status_vs_Stroke))), col=c("lightcyan","lightblue","blue","navyblue"),names.arg=c("absent","present"), legend=c("formerly smoked","never smoked","smokes","unknown"), args.legend = list(title = "Smoking status", x="topright"), beside= TRUE)
text(x=z,y=Smoking_status_vs_Stroke + 100.0,labels=Smoking_status_vs_Stroke)

```

Chunk 16:
```{r}
#Plotting relation between marriage status and stroke.

Stroke_dataset$ever_married <- as.factor(Stroke_dataset$ever_married)
Stroke_dataset$ever_married <- as.numeric(Stroke_dataset$ever_married)

Marriage_vs_Stroke <- table(Stroke_dataset$ever_married,Stroke_dataset$stroke)
Marriage_vs_Stroke
M <- barplot(Marriage_vs_Stroke, main="Relation between marriage status and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Marriage_vs_Stroke))), col=c("red","yellow"),names.arg=c("absent","present"), legend=c("No","Yes"), args.legend = list(title = "Ever Married", x="topright"), beside= TRUE)
text(x=M,y=Marriage_vs_Stroke + 200.0,labels=Marriage_vs_Stroke)

```

Chunk 17:
```{r}
#Plotting relation between working status and stroke.

Stroke_dataset$work_type <- as.factor(Stroke_dataset$work_type)
Stroke_dataset$work_type <- as.numeric(Stroke_dataset$work_type)

Work_type_vs_Stroke <- table(Stroke_dataset$work_type,Stroke_dataset$stroke)
Work_type_vs_Stroke
WT <- barplot(Work_type_vs_Stroke, main="Relation between working status and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Work_type_vs_Stroke))), col=rainbow(5),names.arg=c("absent","present"), legend=c("child","government job","never worked","private","self-employed"), args.legend = list(title = "Working status", x="topright"), beside= TRUE)
text(x=WT,y=Work_type_vs_Stroke + 100.0,labels=Work_type_vs_Stroke)

```

Chunk 18:
```{r}
#Plotting relation between residence type and stroke.

Stroke_dataset$Residence_type <- as.factor(Stroke_dataset$Residence_type)
Stroke_dataset$Residence_type <- as.numeric(Stroke_dataset$Residence_type)

Residence_vs_Stroke <- table(Stroke_dataset$Residence_type,Stroke_dataset$stroke)
Residence_vs_Stroke
R <- barplot(Residence_vs_Stroke, main="Relation between residence type and stroke", xlab="Stroke", ylab="No. of patients",ylim=range(pretty(c(0,Residence_vs_Stroke))), col=c("grey","black"),names.arg=c("absent","present"), legend=c("Rural","Urban"), args.legend = list(title = "Residence", x="topright"), beside= TRUE)
text(x=R,y=Residence_vs_Stroke + 200.0,labels=Residence_vs_Stroke)

```

Chunk 19:
```{r}
#Plotting relation between bmi and stroke.

Stroke_dataset_bmi_adults <- Stroke_dataset[Stroke_dataset$age>20 & Stroke_dataset$age<=85,]
Stroke_dataset_bmi_adults

Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi<18.5]="underweight"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=18.5 & Stroke_dataset_bmi_adults$bmi<25]="healthy"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=25 & Stroke_dataset_bmi_adults$bmi<30]="overweight"
Stroke_dataset_bmi_adults$bmi_cat[Stroke_dataset_bmi_adults$bmi>=30]="obese"

BMI_vs_Stroke <- table(Stroke_dataset_bmi_adults$bmi_cat,Stroke_dataset_bmi_adults$stroke)
BMI_vs_Stroke
bmi <- barplot(BMI_vs_Stroke, main="Relation between BMI and stroke",xlab="Stroke",ylim=range(pretty(c(0,BMI_vs_Stroke))),col=c("pink","orange","red","yellow"),names.arg=c("absent","present"), legend=TRUE , args.legend = list(title = "BMI", x="topright"), beside= TRUE)
text(x=bmi,y=BMI_vs_Stroke + 100.0,labels=BMI_vs_Stroke)

```

Chunk 20:
```{r}
#Applying chi-square test to find an association between different categorical independent variables and the dependent variable(stroke).
#Gender vs Stroke

chisq.test(Stroke_dataset$gender,Stroke_dataset$stroke)

```

Chunk 21:
```{r}
#Hypertension vs Stroke

chisq.test(Stroke_dataset$hypertension,Stroke_dataset$stroke)

```

Chunk 22:
```{r}
#Heart disease vs Stroke

chisq.test(Stroke_dataset$heart_disease,Stroke_dataset$stroke)

```

Chunk 23:
```{r}
#Marriage status vs Stroke

chisq.test(Stroke_dataset$ever_married,Stroke_dataset$stroke)

```

Chunk 24:
```{r}
#Working status vs Stroke

chisq.test(Stroke_dataset$work_type,Stroke_dataset$stroke)

```

Chunk 25:
```{r}
#Residence type vs Stroke

chisq.test(Stroke_dataset$Residence_type,Stroke_dataset$stroke)

```

Chunk 26:
```{r}
#Smoking status vs Stroke

chisq.test(Stroke_dataset$smoking_status,Stroke_dataset$stroke)

```

Chunk 27:
```{r}
#Finding correlation between different continuous independent variables and the dependent variable(stroke).
#Age vs Stroke

cor.test(Stroke_dataset$age,Stroke_dataset$stroke)

```

Chunk 28:
```{r}
#BMI vs Stroke

cor.test(Stroke_dataset$bmi,Stroke_dataset$stroke)

```

Chunk 29:
```{r}
#Diabetes vs Stroke

cor.test(Stroke_dataset$avg_glucose_level,Stroke_dataset$stroke)

```

Chunk 30:
```{r}
#Correlation matrix

Stroke_dataset <- read.csv("/Users/nehabhasin/Desktop/HS631-STATS/PREDICTION OF STROKE_PROJECT/prediction_of_stroke-project_1/data/Stroke_dataset.csv",header = TRUE, sep = ",")
colSums(is.na(Stroke_dataset))
Stroke_dataset$bmi[is.na(Stroke_dataset$bmi)] <- 0
Stroke_dataset$bmi[Stroke_dataset$bmi==0] <- sample(23.50:28.89,replace=TRUE)

Stroke_dataset$gender <- as.factor(Stroke_dataset$gender)
Stroke_dataset$ever_married <- as.factor(Stroke_dataset$ever_married)
Stroke_dataset$work_type <- as.factor(Stroke_dataset$work_type)
Stroke_dataset$Residence_type <- as.factor(Stroke_dataset$Residence_type)
Stroke_dataset$smoking_status <- as.factor(Stroke_dataset$smoking_status)

Stroke_dataset$smoking_status <- as.numeric(Stroke_dataset$smoking_status)
Stroke_dataset$gender <- as.numeric(Stroke_dataset$gender) 
Stroke_dataset$ever_married <- as.numeric(Stroke_dataset$ever_married)
Stroke_dataset$work_type <- as.numeric(Stroke_dataset$work_type)
Stroke_dataset$Residence_type <- as.numeric(Stroke_dataset$Residence_type)

any(is.na(Stroke_dataset))

rcorr(as.matrix(Stroke_dataset[,2:12]))

Matrix_Stroke <- cor(Stroke_dataset[,2:12])
Matrix_Stroke
corrplot(Matrix_Stroke, method="circle",type="lower",tl.col="black")

```

Chunk 31:
```{r}
#Plotting the different variables
#Plot the axis

plot(Stroke_dataset$hypertension,Stroke_dataset$age,main="Presence/Absence of Hypertension \nbased on age",xlab="Hypertension",ylab="Age")
plot(Stroke_dataset$heart_disease,Stroke_dataset$age,main="Presence/Absence of Heart disease \nbased on age",xlab="Heart disease",ylab="Age")
plot(Stroke_dataset$stroke,Stroke_dataset$age,main="Presence/Absence of Stroke \nbased on age",xlab="Stroke",ylab="Age")
plot(Stroke_dataset$stroke,Stroke_dataset$OnAdmit_heartRate,main="Presence/Absence of Stroke \nbased on heart rate",xlab="Stroke",ylab="Heart rate")

```
Chunk 32:
```{r}
#Plotting all continuous variables.

ggplot(data=Stroke_dataset,aes(x=age)) + geom_density() + ggtitle("Plot of Age") +
  xlab("Age (yrs)") 
ggplot(data=Stroke_dataset,aes(x=bmi)) + geom_density() + ggtitle("Plot of BMI") +
  xlab("BMI") 
ggplot(data=Stroke_dataset,aes(x=avg_glucose_level)) + geom_density() + ggtitle("Plot of Average Blood Glucose Levels") +
  xlab("Age (mg/dl)") 
ggplot(data=Stroke_dataset,aes(x=sysBP)) + geom_density() + ggtitle("Plot of Systolic BP") +
  xlab("Systolic BP (mmHg)") 
ggplot(data=Stroke_dataset,aes(x=diaBP)) + geom_density() + ggtitle("Plot of Diastolic BP") +
  xlab("Diastolic BP (mmHg)") 
ggplot(data=Stroke_dataset,aes(x=OnAdmit_heartRate)) + geom_density() + ggtitle("Plot of Heart Rate on admission") +
  xlab("Heart rate (beats/min)") 

```
Chunk 33:
```{r}

Stroke_dataset$logbmi <- log(Stroke_dataset$bmi)
Stroke_dataset$logglucose <- log(Stroke_dataset$avg_glucose_level-45)####iterated to 45 for alteast normal distribution
#######
#plotting for combination nominal variables (smoking staus, bmi)
ggplot(data=Stroke_dataset,aes(x=smoking_status,fill=stroke)) + geom_histogram(stat="count")
ggplot(data=Stroke_dataset,aes(x=bmi,fill=stroke)) + geom_density()

```

Chunk 34:
```{r}
#Splitting the data to Train data and test data 

split <- sample.split(Stroke_dataset$stroke, SplitRatio = 0.8)
TrainStroke <- subset(Stroke_dataset,split==TRUE)
TestStroke <- subset(Stroke_dataset,split==FALSE)

stat.desc(TrainStroke, basic = FALSE, norm = TRUE)
stat.desc(TestStroke, basic = FALSE, norm = TRUE)
```

Chunk 35:
```{r}
########
#Identifying correlation
corr = round(cor(Stroke_dataset[,c(3,9,10,13,14,15,16,17)]),2) #rounding to 2 decimal
corr
#none correlated
ggcorrplot(corr,hc.order=TRUE)

```
Chunk 36:
```{r}
#Applying Logistic regression to all independent variables.

strokepredict <- glm(stroke ~ gender + age + hypertension + heart_disease + ever_married + work_type + Residence_type + avg_glucose_level + bmi + smoking_status + sysBP + diaBP + OnAdmit_heartRate, data = Stroke, family="binomial")
summary(strokepredict)
plot(strokepredict) # Review cook's distance plot to identify outlier patients. In this case, there are no outlier patients

rev(sort(round(cooks.distance(strokepredict),2))) # Another way to identify outliers by comparing numerical values of Cook's distance for each patient and sorting them in descending order. In this specific case, there are no outliers.

exp(coef(strokepredict))

```

Chunk 37:
```{r}
#Additional safeguards to eliminate independant variables with high correlation amongst themselves

vif(strokepredict)

```

Chunk 38:
```{r}
#Calculating R2 for Model 1

ll.null <- strokepredict$null.deviance/-2
ll.proposed <- strokepredict$deviance/-2
(ll.null-ll.proposed)/ll.null

1-pchisq(2*(ll.proposed-ll.null),df=(length(strokepredict$coefficients)-1))

```

Chunk 39:
```{r}
#Plotting the model output

predicted.data <- data.frame(probability.of.stroke=strokepredict$fitted.values,stroke = Stroke$stroke)
predicted.data <- predicted.data[order(predicted.data$probability.of.stroke,decreasing=FALSE),]
predicted.data$rank <- 1:nrow(predicted.data)
ggplot(data=predicted.data,aes(x=rank,y=probability.of.stroke))+geom_point(aes(color=stroke),alpha=1,shape=4,stroke=2)

```

Chunk 40:
```{r}
#Model 2
#Interaction effects of variables where it makes logical sense. However, none of the co-efficients of interaction variables are significant.
strokepredict2 <- glm(stroke ~ gender + age + hypertension + heart_disease + ever_married + work_type + Residence_type + avg_glucose_level + bmi + smoking_status + sysBP + diaBP + OnAdmit_heartRate +age*hypertension + age*heart_disease + hypertension*heart_disease + heart_disease*smoking_status + hypertension*OnAdmit_heartRate + age*avg_glucose_level, data = Stroke, family="binomial")
summary(strokepredict2)
```

Chunk 41:
```{r}
#Model 3
#Hence, best fit model is derived by removing all interaction variabbles as well as variables from the first model that are not significant
strokepredict3 <- glm(stroke ~ age + hypertension + avg_glucose_level, data = Stroke, family="binomial")
summary(strokepredict3)
```

Chunk 42:
```{r}
#Model 4
#Improving the model by minimizing AIC value using Step AIC function. This is another method of optimizing best-fit model
Newstrokepredict <- stepAIC (strokepredict)
summary(Newstrokepredict)

anova(strokepredict, strokepredict2, strokepredict3, Newstrokepredict, test = "Chisq")
```

Chunk 43:
```{r}
#Recalculating R2 and P value for the updated model
ll.null <- Newstrokepredict$null.deviance/-2
ll.proposed <- Newstrokepredict$deviance/-2
(ll.null-ll.proposed)/ll.null

1-pchisq(2*(ll.proposed-ll.null),df=(length(Newstrokepredict$coefficients)-1))
```

Chunk 44:
```{r}
#plotting the model output
predicted.data1 <- data.frame(probability.of.stroke=Newstrokepredict$fitted.values,stroke = Stroke$stroke)
predicted.data1 <- predicted.data1[order(predicted.data1$probability.of.stroke,decreasing=FALSE),]
predicted.data1$rank <- 1:nrow(predicted.data1)
ggplot(data=predicted.data1,aes(x=rank,y=probability.of.stroke))+geom_point(aes(color=stroke),alpha=1,shape=4,stroke=2)
summary(Newstrokepredict)
```

Chunk 45:
```{r}
#confusion matrix for the Model1
ResultStroke <- predict(strokepredict,TestStroke,type="response")

confmatrix <- table(Actualvalue=TestStroke$stroke, Predictedvalue = ResultStroke >0.5)
confmatrix

(confmatrix[[1,1]] + confmatrix[[2,2]])/sum(confmatrix)
```

Chunk 46:
```{r}
#confusion matrix for the Model2
ResultStroke <- predict(Newstrokepredict,TestStroke,type="response")

confmatrix <- table(Actualvalue=TestStroke$stroke, Predictedvalue = ResultStroke >0.5)
confmatrix
```

Chunk 47:
```{r}
#Final interpretation of the model - relative chances of getting a stroke
round (exp(coef(Newstrokepredict)),3)

```

Chunk 48:
```{r}
#Calculating Rsquares using logisticpsuedoR2 formula. Output is similar to the R2 we computed earlier in the model
dev <- Newstrokepredict$deviance
nullDev <- Newstrokepredict$null.deviance
modelN <- length(Newstrokepredict$fitted.values)
R.l <- 1 - dev/nullDev
R.cs <- 1 - exp(-(nullDev - dev)/modelN)
R.n <- R.cs/(1 - (exp(-(nullDev/modelN))))
round(R.l,3)
round(R.cs,3)
round(R.n,3)

```

Chunk 49:
```{r}
#Conclusion: People with history of hypertension as well as people with heart disease are relatively more likely (46% and 39% respectively) to experience stroke.
```

